### 2022-05-26 chapters/04-chapter-4.tex
txs auto checkin

Tabel \ref{testcase} akan menjelaskan kasus-kasus pengujian sistem PRA.
\begin{small}
	\begin{adjustwidth}{-2cm}{}
		\begin{longtable}{ | p{1cm} | p{3.5cm} | p{3.5cm} | p{3.5cm} | }
			\caption{Daftar \textit{service} dan fungsi yang akan dimodifikasi}
			\label{testcase}                                                           
			\\ \hline
			\centering\bfseries{No} & \centering\bfseries{Nama Service} & \centering\bfseries{Nama Fungsi} & \centering\bfseries{Metode} \tabularnewline \hline
			\endfirsthead
			1 & AdService &  cookware & hoo \\ \hline

>>>>

Tabel \ref{testcase} akan menjelaskan kasus-kasus pengujian sistem PRA.
\begin{small}
	\begin{adjustwidth}{-3cm}{}
		\begin{longtable}{ | p{1cm} | p{3.5cm} | p{3.5cm} | p{3.5cm} | }
			\caption{Kasus-kasus pengujian}
			\label{testcase}                                                           
			\\ \hline
			\centering\bfseries{ID} & \centering\bfseries{Nama Service} & \centering\bfseries{Nama Fungsi} & \centering\bfseries{Metode} \tabularnewline \hline
			\endfirsthead
			1 & AdService &  cookware & hoo \\ \hline
